---
title: "Getting Started with Scraping"
author: "Kiegan Rice"
date: "June 3, 2017"
output: html_document
---

### Can we find the links to different 'Sets' Home pages on LEGO.com?  



```{r}
#install.packages("rvest")
library(rvest)

url <- "https://shop.lego.com/en-US/Themes"
html <- read_html(url)
theme_links <- html %>% html_nodes(".cat-list__see-products") %>% html_attr(name="href")
theme_links
```

### Great! Now, for a specific group of sets, can we get links to each of the individual set pages?  

We will use 'City' as an example. Test 
```{r}
theme_url <- paste0("https://shop.lego.com", theme_links[4])
theme_url_seeall <- paste0(theme_url,"?S1=&all=2&callback=json&cc=us&count=18&do=json-db&i=1&jsonp=jsonCallback&lang=en&pt=shop&q=*&q1=E2034D52-000A-43AB-A026-06F14E7A23C1&q2=setTypesFacetCategory&rank=rankUS&showRetired=false&sort=sort_flags&sp_q_exact_9=us&x1=theme_id&x2=productType_id")

html_theme <- read_html(theme_url_seeall)
html_theme %>% html_nodes("div") %>% html_attr(name = "href")
bunch_of_text <- html_theme %>% html_nodes("div") %>% html_text()

strsplit(bunch_of_text[224], "ADD TO WISHLIST")

## to get the 'see all' option: 
## https://shop.lego.com/en-US/City-Sets?S1=&all=2&callback=json&cc=us&count=18&do=json-db&i=1&jsonp=jsonCallback&lang=en&pt=shop&q=*&q1=E2034D52-000A-43AB-A026-06F14E7A23C1&q2=setTypesFacetCategory&rank=rankUS&showRetired=false&sort=sort_flags&sp_q_exact_9=us&x1=theme_id&x2=productType_id
```

This is where it starts getting messy! So this will probably be the tricky part of getting an automated function. It would be easier if we knew the name of the specific set and had the identifying number, but nothing is ever quite that easy.  
